---
title: "Research Innovation & Evaluation"
listing:
  contents: posts
  sort: "date desc"
  type: default
  categories: true
  sort-ui: false
  filter-ui: false
page-layout: full
title-block-banner: true
---

## This is a summary of past and current projects happening at Northwood, take a look around!

### Current and Past Project Status 

```{r setup, include=FALSE}

library (echarts4r)
library(dplyr)
library(tidyr)
library(knitr)
library (shiny)
library (reactable)
knitr::opts_chunk$set(echo = TRUE)

DB <- read.csv ('C:/Users/andre/Desktop/R/NW/NW/myblog/BySchool.csv')
DB$Year <- as.factor (DB$Year)

Year <- c ("15/16", "16/17", "17/18", "18/19", "19/20","20/21", "21/22")
Total <- c (8, 11, 6, 6, 6, 10, 15)
LTC <- c (3, 6, 5, 4, 2, 8, 11)
Com <- c (3, 3, 1, 1, 3, 2, 3)
Corp <- c (2, 2, 0, 1, 1, 0, 1)
Year <- data.frame(Year, Total, LTC, Com, Corp) 
View (Year)
Year_long <- gather (Year, "LTC":"Corp", key = "Population", value = "Active")
```
<br> 

All these active projects can be categorized into projects withing our Long-term Care Facilities, our Community-based Older Adults, and within the Corporation itself. This graph demonstrates which group projects fall into by year. 

<br> 

```{r All Studies}
#| echo: false
reactable (Year_long, 
           columns = list (
             Total = colDef(align = "center"), 
             Population = colDef (align = "center"), 
             Active = colDef(align = "center")
           ), 
           highlight = TRUE, 
           searchable = TRUE
           )
```

```{r, fig.align='center'}
#| echo: false
Figure <- 
  Year %>%  
  e_charts (x = Year) %>% 
  e_line (serie = Total) %>% 
  e_area (LTC) %>% 
  e_area (Corp) %>% 
  e_area (Com) %>% 
  e_axis_labels (x = "Year", 
                 y = "Active Projects") %>% 
  e_title ("Active Projects by Year & Population") %>% 
  e_theme ("infographic") %>% 
  e_legend (right = 0) %>% 
  e_tooltip (
    trigger = "axis", 
    backgroundColor = "rgba(255, 255, 255, 1)") 
Figure
```

```{r, echo=FALSE, fig.align='center'}
Figure2 <- 
  DB %>% 
  group_by(University) %>% 
  e_chart (x = Year, stack = "grp") %>% 
  e_bar (N) %>% 
  e_legend (type = ("scroll"), 
            left = 0, 
            bottom = 0) %>% 
  e_theme ("infographic") %>% 
  e_tooltip (
    trigger = "axis", 
    backgroundColor = "rgba(255, 255, 255, 1)")  %>% 
  e_title(
    text = "Research Projects by Year and Institution"
  ) %>% 
  e_y_axis(
    splitArea = list(show = FALSE),
    splitLine = list(show = FALSE)
  )
  
Figure2
```
  

This document was last updated on `r Sys.Date ()`




















